---
title: "Avocado Prices Project"
author: "D.O. A.S."
date: "Fall 2018"
output:
  html_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    keep_tex: yes
    toc: yes
    toc_depth: 2
geometry: right=2.5in
---


```{r cache=FALSE, echo=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=5.5, fig.width=6, collapse=TRUE, comment="", prompt=TRUE)
options(width=63)
```

dplyr reference: https://dplyr.tidyverse.org/reference/index.html

#Read Data

Some relevant columns in the dataset: (copied from https://www.kaggle.com/neuromusic/avocado-prices/home)

 * Date - The date of the observation
 * AveragePrice - the average price of a single avocado
 * type - conventional or organic
 * year - the year
 * Region - the city or region of the observation
 * Total Volume - Total number of avocados sold
 * 4046 - Total number of avocados with PLU 4046 sold (small Hass)
 * 4225 - Total number of avocados with PLU 4225 sold (large Hass)
 * 4770 - Total number of avocados with PLU 4770 sold (extra large Hass)

```{r}
avocado <- read.csv('avocado.csv', header = TRUE)
avo <- avocado[, c('Date', 'AveragePrice', 'Total.Volume', 'type', 'year', 'region')]
head(avo)
dim(avo)
str(avo)
```
#Select Data
```{r}
date <- avo[,1]
ave <- avo[,2]
vol <- avo[,3]
type <- avo[,4]
year <- avo[,5]
region <- avo[,6]
max_ave <- max(avo$AveragePrice)
max_ave
min_ave <- min(avo$AveragePrice)
min_ave
imax_ave <- which.max(avo$AveragePrice)
imax_ave 
imin_ave <- which.min(avo$AveragePrice)
imin_ave
avo$region[imax_ave]
avo$region[imin_ave]
mean_ave <- mean(avo$AveragePrice)
mean_ave
```
# Filter Data
```{r}
library(dplyr)
avo <- mutate(avo,rate=ave/vol*100000)
avop_f <- filter(avo, AveragePrice >= 1.41)
head(avop_f)
avor_f <- filter(avo,rate >= 1.5)
by_avo <- group_by(avo, region)

```
#Summarize 
```{r}
summarize(avo,Ave_avo = mean(AveragePrice), med_avo = median(AveragePrice), ave_vol = mean(Total.Volume), med_vol = median(Total.Volume))
  
```