---
title: "Avocado Prices Project"
author: "D.O. A.S."
date: "Fall 2018"
output:
  html_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    keep_tex: yes
    toc: yes
    toc_depth: 2
geometry: right=2.5in
---


```{r cache=FALSE, echo=FALSE}
library(knitr)
opts_chunk$set(fig.align="center", fig.height=5.5, fig.width=6, collapse=TRUE, comment="", prompt=TRUE)
options(width=63)
```

dplyr reference: https://dplyr.tidyverse.org/reference/index.html

#Read Data

Some relevant columns in the dataset: (copied from https://www.kaggle.com/neuromusic/avocado-prices/home)

 * Date - The date of the observation
 * AveragePrice - the average price of a single avocado
 * type - conventional or organic
 * year - the year
 * Region - the city or region of the observation
 * Total Volume - Total number of avocados sold
 * 4046 - Total number of avocados with PLU 4046 sold (small Hass)
 * 4225 - Total number of avocados with PLU 4225 sold (large Hass)
 * 4770 - Total number of avocados with PLU 4770 sold (extra large Hass)

```{r}
avocado <- read.csv('avocado.csv', header = TRUE)
head(avocado)
dim(avocado)
str(avocado)
```
